Gaussian process

### 2023-07-10 stats/gaussianprocess.Rmd
update gaussian process models

mgp_aggregated <- brm(mean_imprecision ~ gp(age_centered, k=50, c=5/4, scale=TRUE),
                    data = mdata,
                    family = lognormal(),
                    warmup = 5000, 
                    iter   = 20000, 
                    chains = 4, 
                    cores  = 4, 
                    threads = threading(8), 
                    control = list(adapt_delta = 0.95), 
                    backend = "cmdstanr")

@@

>>>>

mgp_aggregated <- brm(mean_imprecision ~ gp(age_centered, k=50, c=5/4, scale=TRUE),
                    data = mdata_aggregated,
                    family = lognormal(),
                    warmup = 5000, 
                    iter   = 20000, 
                    chains = 4, 
                    cores  = 4, 
                    threads = threading(8), 
                    control = list(adapt_delta = 0.95), 
                    backend = "cmdstanr")

@@

```{r compare_models}
nd_triallevel <- mdata %>% 
  select(-c(imprecision, click_dist_balloons)) %>% 
  mutate(symmetric_position = 0, trial_nr = 0)

pred_triallevel <- fitted(mgp_triallevel, newdata = nd_triallevel, re_formula = NA) %>% as_tibble() %>% bind_cols(nd_triallevel)

# same for aggregate

nd_aggregated <- mdata_aggregated %>% 
  select(-c(mean_imprecision))

pred_aggregated <- fitted(mgp_aggregated, newdata = nd_aggregated, re_formula = NA) %>% as_tibble() %>% bind_cols(nd_aggregated)

pred_combined <-full_join(pred_aggregated %>% mutate(model = "subject level"), pred_triallevel %>% mutate(model = "trial level"))

# plot

ggplot() +

  geom_smooth(
    data = pred_combined, 
    aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5, group = model, col = model), 
    stat = "identity", size = 0.5, alpha = 0.15
  ) 
```

```{r aggregated_plot}
ggplot() +

  geom_jitter(
    data = mdata_aggregated, 
    aes(x = age, y = mean_imprecision), 
    col = "darkgrey", alpha = 0.75
  ) +

  geom_smooth(
    data = pred_aggregated, 
    aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5), 
    stat = "identity", size = 1, alpha = 0.15, fill = "#006C66", col = "#006C66",
  ) +

  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) +

  labs(x = "Age in years", y = "Average imprecision in target width")
```
